\section*{Message from the Program Committee Co-Chairs}
\thispagestyle{emptyheader}
%\renewcommand{\large}{\fontsize{9}{11}\selectfont}
% that's a hack to make this part nicely fill the pages

\setlength{\parskip}{.7ex}
%\setlength{\parindent}{0pt}

The Conference on Computational Natural Language Learning (CoNLL) is
an annual meeting organized by SIGNLL, the ACL special interest group
on natural language learning. CoNLL-2014 is the eighteenth meeting in
this series and will be held in Baltimore, Maryland, USA on June
26-27, 2014, in conjunction with ACL-2014.

In the main session of CoNLL, we invited papers on all aspects of
computational approaches to natural language learning, as well as on
machine reading, the special topic of interest this year. We received
90 submissions, of which 7 were eventually withdrawn, and accepted 20
of the remaining 83 papers. The final version of each accepted paper
was allowed nine content pages plus two pages with only bibliographic
references.

As in previous years, CoNLL-2014 hosts a high-profile NLP shared task,
Grammatical Error Correction, a continuation of the shared task in
2013. Papers of the shared task are collected in a companion volume of
the CoNLL-2014 proceedings.

Similar to the arrangement in last year, each accepted paper in
CoNLL-2014 will be given an 18 minute oral presentation slot, as well
as a poster. There will be a poster session in the afternoon of each
day, consisting of papers presented orally earlier on the same
day. The shared task posters will also participate in the same poster
session on Day 1.

We thank all of the authors who submitted their work to CoNLL-2014, as
well as the program committee for helping us select from among the
many strong submissions. We are also grateful to our invited speakers,
Morten Christiansen and Tom Mitchell, who graciously agreed to give
talks at CoNLL. Special thanks to the best paper award committee
members, Walter Daelemans, Joakim Nivre and Dan Roth, who helped
choose the best paper winner. Also thanks to Xavier Carreras and
Alexander Clark, for their valuable advice, to the SIGNLL information
officer, Erik Tjong Kim Sang, for publicity and to Ben Verhoeven for
maintaining the CoNLL Web site. We also appreciate the additional help
we received from the ACL program chairs, workshop chairs, and
publication chairs.

Finally, many thanks to Microsoft Research and Google for sponsoring
CoNLL-2014. We hope you enjoy the conference!

\vspace{.2in}
\indent Roser Morante and Scott Wen-tau Yih\\
\indent CoNLL 2014 Conference Chairs
