\begin{bio}
\small
{\bfseries Dr. Deyi Xiong} is a professor at Sochoow University. His research interests are in the area of natural language processing, particularly statistical machine translation and parsing. Previously he was a research scientist at the Institute for Infocomm Research of Singapore. He received the B.Sc degree from China University of Geosciences (Wuhan, China) in 2002, the Ph.D.degree from the Institute of Computing Technology (Beijing, China) in 2007, both in computer science. He has published papers in prestigious journals and conferences on statistical machine translation, including Computational Linguistics, IEEE TASLP, JAIR, NLE, ACL, EMNLP, AAAI and IJCAI. He was the program co-chair of IALP 2012 and CLIA workshop 2011.

{\bfseries Dr. Min Zhang, a }distinguished professor and Director of the Research Center of Human Language Technology at Soochow University (China), received his Bachelor degree and Ph.D. degree in computer science from Harbin Institute of Technology in 1991 and 1997, respectively. From 1997 to 1999, he worked as a postdoctoral research fellow in Korean Advanced Institute of Science and Technology in South Korea. He began his academic and industrial career as a researcher at Lernout & Hauspie Asia Pacific (Singapore) in Sep. 1999. He joined Infotalk Technology (Singapore) as a researcher in 2001 and became a senior research manager in 2002. He joined the Institute for Infocomm Research (Singapore) as a research scientist in Dec. 2003. He joined the Soochow University as a distinguished professor in 2012.

His current research interests include machine translation, natural language processing, information extraction, social network computing and Internet intelligence. He has co-authored more than 150 papers in leading journals and conferences, and co-edited 10 books/proceedings published by Springer and IEEE. He was the recipient of several awards in China and oversea. He is the vice president of COLIPS (2011-2013), the elected vice chair of SIGHAN/ACL (2014-2015), a steering committee member of PACLIC (2011-now), an executive member of AFNLP (2013-2014) and a member of ACL (since 2006). He supervises Ph.D students at National University of Singapore, Harbin Institute of Technology and Soochow University.
\end{bio}

\begin{tutorial}{Semantics, Discourse and Statistical Machine Translation}
  {Deyi Xiong (Sochoow University), Min Zhang (Sochoow University)}
  {Sunday, June 22, 2014, 2:00--5:30pm}
  {\TutLocG}
