\section{Message from the Program Committee Co-Chairs}
\setheaders%
    {Message from the Program Committee Co-Chairs}%
    {Message from the Program Committee Co-Chairs}
\thispagestyle{emptyheader}
%\renewcommand{\large}{\fontsize{9}{11}\selectfont}
% that's a hack to make this part nicely fill the pages
\begin{large}

\setlength{\parskip}{.7ex}
%\setlength{\parindent}{0pt}

Welcome to the 2014 Conference of the Association for Computational
Linguistics! This year ACL received 572 long paper submissions and 551
short paper submissions. Of the long papers, 146 were accepted for
presentation at ACL --- 95 as oral, and 51 as poster
presentations. 139 short papers were accepted --- 51 as oral, and 88
as poster presentations.

The submissions were reviewed under different categories and using
different review forms for empirical/data-driven, theoretical,
applications/tools, resources/evaluation, and survey papers. For the
short papers we additionally used a negative results category and were
glad to see that the community is becoming more open to enabling the
publication of useful negative results.

Based on feedback from prior years, this year we organized the posters
in two large poster sessions to accommodate the growing number of
high-quality submissions accepted in poster presentation format. We
hope attendees and authors will benefit from this additional time to
present and discuss ideas.  Another innovation we are experimenting
with this year is to optimize the conference schedule based on
feedback from attendees on the talks they would like to see. We
collected attendee responses using a scheduling survey developed with
the help of David Yarowsky and Svitlana Volkova (thanks to the 338
volunteers who completed the survey!), and we optimized the conference
schedule to assign popular sessions to large conference rooms, and to
reduce the chance that two talks that an attendee is interested in are
scheduled at the same time.  Additionally, as in NAACL 2013, all talks
will be recorded and made available for future viewing.

ACL 2014 will have two distinguished invited speakers. Corinna Cortes
(Head of Google Research, NY) and Zoran Popovi\'{c} (Director of
Center for Game Science, University of Washington).

There are many individuals to thank for their contributions to ACL
2014. We would like to thank the thirty three area chairs for their
hard work on recruiting reviewers, leading the discussion process, and
carefully ranking the submissions.  We would like to thank Mark Dredze
for developing and sharing a reviewer assignment tool, that was used
at ACL this year. It was applied to ACL reviewing with the help of
Jiang Guo and the area chairs who provided feedback at several stages
of the process. We would also like to thank the seven hundred and
seventy nine reviewers and seventy two secondary reviewers on whose
efforts we depend to select high-quality and timely scientific
work. This year we specifically acknowledged around 14\% of the
reviewers who went the extra mile and provided extremely helpful to
the area chairs and authors reviews (their names are marked with a *
in the organization section of the proceedings). The ACL coordinating
committee members, including Dragomir Radev, Jian Su, Graeme Hirst,
Hal Daum\'{e} III, Chris Callison-Burch, and Haifeng Wang were very
helpful on various issues relating to the organization.  We would like
to thank the prior conference chairs Jason Eisner, Hal Daum\'{e}, Lucy
Vanderwende, Jian Su, Rada Mihalcea, Marius Pasca, Pascale Fung, and
Massimo Poesio for their advice. We are very grateful for the guidance
and support of the general chair Daniel Marcu, to the ACL Business
Manager Priscilla Rasmussen who knew practically everything, to the
local chair David Yarowsky, the publication chairs Yusuke Miyao and
Alexander Koller, and to Matt Post who stepped in to handle the
conference handbook. We would also like to thank Jiang Guo who helped
with reviewer assignment and numerous other tasks. Rich Gerber from
Softconf was extremely responsive to all of our requests, and we are
grateful for that.

We hope you will enjoy ACL 2014 in Baltimore!

\vspace{.2in}
ACL 2014 Program Co-Chairs\\
\indent Kristina Toutanova, Microsoft Research\\
\indent Hua Wu, Baidu

%\cleardoublepage
\end{large}
%\renewcommand{\large}{\fontsize{10}{12}\selectfont}
